What Can Stack Traces Tell us about Exceptions in Java?

### 2014-07-07 android-stacks.tex
more changes on Introduction

In [ref] defined a set of characteristics a good bug issue should have. They showed that among 
the most important relevant information are: (1) steps to reproduce the bug; 
(2) and the failure stack trace.

A typical stack trace consists of an ordered list of methods that
were active on the call stack before the failure occurred. Stack traces
are a useful source of information about system crashes, and are often used to
support developers in debugging~\cite{schroter2010stack}. Moreover, information
from stack traces combined with crash and bug reports can be used to support bug
classification and clustering~\cite{wang2013improving, kim2011crash,
dhaliwal2011classifying}, fault-proneness prediction
models~\cite{kim2013predicting} and even automated bug
fixing~\cite{sinha2009fault} tools.

We could observe that existing research has focused on the analysis of a 
single system at a time. Moreover, the search facilities of repositories are very limited, also
enabling the analysis of a single project.

Modern applications have to cope with similar and increasing number of abnormal
computation states that arise as a consequence of faults in the application
itself (e.g., access of null references), noisy user inputs or faults in
underlying middleware or hardware. The exception handling mechanism~\cite{goodenough1975exception} is one of the most used schemes for detecting and recovering from such exceptional conditions.

@@

-----
Along the recent years we have witnessed a rapid increase in 
the number of social applications on the Web. Applications which 
allow their users to track the activities of a large number 
of others regardless of his/her location and affiliation.

This tendency can also be seen on the software development context 
where Github emerged and became an extensively used social coding 
platform. Github alows developers to create and maintain opensource 
projects relying  on Git distributed version control, and provides a set 
of tools which allow the information about developers and their activities
 to be visible within and across open souce projects.

Among those tools there is the Github issue tracking system, which makes
issues related to new, features, bugs and general comments publicly available.

-----

>>>>

One of the most important elements of a crash report genereted eigther manually
or automatically is the failure stack trace [ref-paper], which tipically consists 
of an ordered list of methods that were active on the call stack before the failure occurred.

Modern applications have to cope with similar and increasing number of sources of failures
 that arise as a consequence of faults in the application
itself (e.g., access of null references), noisy user inputs or faults in
underlying middleware or hardware.   The exception handling 
mechanism~\cite{goodenough1975exception}, been embedded in several 
programming languages (e.g. Java, C++, C\#), is one of the most used
 schemes for detecting and recovering from such failures.

Such exception stack traces are a useful source of 
information about system crashes, and are often used to
support developers in debugging~\cite{schroter2010stack}. Moreover, information
from stack traces combined with crash and bug reports can be used to support bug
classification and clustering~\cite{wang2013improving, kim2011crash,
dhaliwal2011classifying}, fault-proneness prediction
models~\cite{kim2013predicting} and even automated bug
fixing~\cite{sinha2009fault} tools.

However existing research has focused on the analysis of a 
single system at a time. Moreover, the search facilities of repositories are very limited, also
enabling the analysis of a single project.

@@

....... OLD VERSION ......
